Outflows and rotation in Lyman alpha emitting galaxies

### 2017-04-04 paper/paper.tex
title

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title[Outflows and rotation in LAEs]{
Outflows and rotation in Lyman alpha galaxies}
\author[M.C. Remolina-Gutierrez \& J.E. Forero-Romero]{
  Maria Camila Remolina-Guti\'errez$^1$ \&
  Jaime E. Forero-Romero $^{1}$ \thanks{je.forero@uniandes.edu.co}\\
  %%
  $^1$ Departamento de F\'isica, Universidad de los Andes, Cra. 1
  No. 18A-10 Edificio Ip, CP 111711, Bogot\'a, Colombia \\
}

@@

@@

These 3 parameters, vrot, vout and tauh, leave the idea of a model of LAE, that although simple, considers the main galaxy's dynamics. All of them have been previously proposed and used by different authors, but never combined together (\cite{Adams72}, \cite{Harrington73}, \cite{Neufeld90}, \cite{Dijkstra06}, \cite{Verhamme06}, \cite{Forero12}, \cite{Martin2015}, \cite{Garavito14}, \cite{Neufeld91}, \cite{Laursen09}, \cite{Barnes11}, \cite{Verhamme12}, \cite{Yajima12}).\\

@@

\subsection{Galaxy's Viewing Angle}
An observer located far away, only receives photons emitted along its line of sight. That means, only photons escaping in the direction of the observer must be counted in the spectrum. In the simulation we approximate this by taking into account only the photons with escaping direction angle $\theta$ respect to the rotation axis within the range $[\theta_{min}-\theta_{max}]$. We illustrate this in Fig. \ref{fig:model}. \\

>>>>

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title[Outflows and rotation in LAEs]{
Outflows and rotation in Lyman alpha emitting galaxies}
\author[M.C. Remolina-Gutierrez \& J.E. Forero-Romero]{
  Maria Camila Remolina-Guti\'errez$^1$ \&
  Jaime E. Forero-Romero $^{1}$ \thanks{je.forero@uniandes.edu.co}\\
  %%
  $^1$ Departamento de F\'isica, Universidad de los Andes, Cra. 1
  No. 18A-10 Edificio Ip, CP 111711, Bogot\'a, Colombia \\
}

@@

Rotation induces two main effects on the \lya line morphology.
First. Break of spherical symmetry due to the 
  preferential direction introduced by the rotation axis.
  This symmetry break is reflected in the observed spectra as a
  dependency on the viewing angle, $\theta$, between the line of sight
  of a distant observer and the rotaional velocity.    
Second. Line blurring as the rotational velocity increases.
  At a fixed viewing angle, faster rotation induces makes the observed
  line wider and increases the flux around the line's center.

\cite{Garavito14} presented in the Appendix an analytical model that
accounts for these two features.
The basic assumption of the analytical model is that each
differential surface element on the sphere Doppler shifts the photons
that it emmits.

@@

These 3 parameters, vrot, vout and tauh, leave the idea of a model of
LAE, that although simple, considers the main galaxy's dynamics. All
of them have been previously proposed and used by different authors,
but never combined together (\cite{Adams72}, \cite{Harrington73}, \cit
e{Neufeld90}, \cite{Dijkstra06}, \cite{Verhamme06}, \cite{Forero12},
\cite{Martin2015}, \cite{Garavito14}, \cite{Neufeld91},
\cite{Laursen09}, \cite{Barnes11}, \cite{Verhamme12},
\cite{Yajima12}).\\

@@

\subsection{Galaxy's Viewing Angle}
An observer located far away, only receives photons emitted along its
line of sight. That means, only photons escaping in the direction of
the observer must be counted in the spectrum. In the simulation we
approximate this by taking into account only the photons with escaping
direction angle $\theta$ respect to the rotation axis within the range
$[\theta_{min}-\theta_{max}]$.

We illustrate this in
Fig. \ref{fig:model}. \\
